---
title: "video_views_growth_rate"
author: "Chongxuan Bi"
date: "1/1/2021"
output: pdf_document
---

# Load in Libraries

```{r}
library(ISLR)
library(mclust)
library(caret)
library(tree)
library(rattle)
library(randomForest)
library(readr)
library(glmnet)
library(gbm)
library(rpart)
library(leaps)
library(pls)
library(stringr)
library(ggplot2)
library(reshape2)
```

# Read in Data

```{r}
training <- read_csv("training.csv")
testing <- read_csv("test.csv")
```

# Preprocessing

## Combine Binary Variables in Training

```{r}
training$avg_growth = c(rep(0,nrow(training)))
training$Num_Views_Base = c(rep(0,nrow(training)))
training$Num_Subscribers_Base = c(rep(0,nrow(training)))
training$count_vids = c(rep(0,nrow(training)))
for (i in 1:nrow(training)) {
  if(training$avg_growth_low[i] == 1){
    training$avg_growth[i] = 1
  } else if (training$avg_growth_low_mid[i] == 1){
    training$avg_growth[i] = 2
  }else if (training$avg_growth_mid_high[i] == 1){
    training$avg_growth[i] = 3
  }
  
  if(training$Num_Views_Base_low[i] == 1){
    training$Num_Views_Base[i] = 1
  } else if (training$Num_Views_Base_low_mid[i] == 1){
    training$Num_Views_Base[i] = 2
  }else if (training$Num_Views_Base_mid_high[i] == 1){
    training$Num_Views_Base[i] = 3
  }
  
  if(training$Num_Subscribers_Base_low[i] == 1){
    training$Num_Subscribers_Base[i] = 1
  } else if (training$Num_Subscribers_Base_low_mid[i] == 1){
    training$Num_Subscribers_Base[i] = 2
  }else if (training$Num_Subscribers_Base_mid_high[i] == 1){
    training$Num_Subscribers_Base[i] = 3
  }
  
  if(training$count_vids_low[i] == 1){
    training$count_vids[i] = 1
  } else if (training$count_vids_low_mid[i] == 1){
    training$count_vids[i] = 2
  }else if (training$count_vids_mid_high[i] == 1){
    training$count_vids[i] = 3
  }
}
training$avg_growth = factor(training$avg_growth)
training$Num_Views_Base = factor(training$Num_Views_Base)
training$Num_Subscribers_Base = factor(training$Num_Subscribers_Base)
training$count_vids = factor(training$count_vids)
```

## Combine Binary Variables in Testing

```{r}
testing$'avg_growth' = c(rep(0,nrow(testing)))
testing$'Num_Views_Base' = c(rep(0,nrow(testing)))
testing$'Num_Subscribers_Base' = c(rep(0,nrow(testing)))
testing$'count_vids' = c(rep(0,nrow(testing)))
for (i in 1:nrow(testing)) {
  if(testing$avg_growth_low[i] == 1){
    testing$avg_growth[i] = 1
  } else if (testing$avg_growth_low_mid[i] == 1){
    testing$avg_growth[i] = 2
  }else if (testing$avg_growth_mid_high[i] == 1){
    testing$avg_growth[i] = 3
  }
  
  if(testing$Num_Views_Base_low[i] == 1){
    testing$Num_Views_Base[i] = 1
  } else if (testing$Num_Views_Base_low_mid[i] == 1){
    testing$Num_Views_Base[i] = 2
  }else if (testing$Num_Views_Base_mid_high[i] == 1){
    testing$Num_Views_Base[i] = 3
  }
  
  if(testing$Num_Subscribers_Base_low[i] == 1){
    testing$Num_Subscribers_Base[i] = 1
  } else if (testing$Num_Subscribers_Base_low_mid[i] == 1){
    testing$Num_Subscribers_Base[i] = 2
  }else if (testing$Num_Subscribers_Base_mid_high[i] == 1){
    testing$Num_Subscribers_Base[i] = 3
  }
  
  if(testing$count_vids_low[i] == 1){
    testing$count_vids[i] = 1
  } else if (testing$count_vids_low_mid[i] == 1){
    testing$count_vids[i] = 2
  }else if (testing$count_vids_mid_high[i] == 1){
    testing$count_vids[i] = 3
  }
}
testing$avg_growth = factor(testing$avg_growth)
testing$Num_Views_Base = factor(testing$Num_Views_Base)
testing$Num_Subscribers_Base = factor(testing$Num_Subscribers_Base)
testing$count_vids = factor(testing$count_vids)
```

## Training Date Split

```{r}
date = str_extract(training$PublishedDate, '[0-9]+[/][0-9]+[/][0-9]+')
date = as.Date(date, '%m/%d/%y')
dow = factor(weekdays(date)) # day of week
hour = as.integer(str_match(training$PublishedDate, '([0-9]+):')[,2])
qod = (hour %/% 4) + 1 # Part of day. 0-4 = 1, 4-8 = 2, 8-12 = 3 etc.
qod = factor(qod)
month = factor(str_match(training$PublishedDate, '([0-9]+)[/][0-9]+[/][0-9]+')[,2])

training$dow = dow
training$qod = qod
training$month = month
```

## Testing Date Split

```{r}
date = str_extract(testing$PublishedDate, '[0-9]+[/][0-9]+[/][0-9]+')
date = as.Date(date, '%m/%d/%y')
dow = factor(weekdays(date))
hour = as.integer(str_match(testing$PublishedDate, '([0-9]+):')[,2])
qod = (hour %/% 4) + 1
qod = factor(qod)
month = factor(str_match(testing$PublishedDate, '([0-9]+)[/][0-9]+[/][0-9]+')[,2])

testing$dow = dow
testing$qod = qod
testing$month = month
```

## Train/Validation Split

```{r}
set.seed(1)
trainIndex <- createDataPartition(training$growth_2_6, p = 0.7, list = FALSE) 
train <- training[trainIndex, ]
valid <- training[-trainIndex, ]

```

## Delete Unrelated Variables/No Variation Columns in Training

```{r}
train_control <- trainControl(method="cv", number = 10) 
# Delete no variation columns 
reduced_train = train[,-c(1, 2)]
reduced_train = reduced_train[,-c(which(colnames(reduced_train) == "max_red"),
                                  which(colnames(reduced_train) == "min_red"),
                                  which(colnames(reduced_train) == "max_green"),
                                  which(colnames(reduced_train) == "min_green"),
                                  which(colnames(reduced_train) == "max_blue"),
                                  which(colnames(reduced_train) == "min_blue"),
                                  which(colnames(reduced_train) == "Num_Subscribers_Base_low"),
                                  which(colnames(reduced_train) == "Num_Subscribers_Base_low_mid"),
                                  which(colnames(reduced_train) == "Num_Subscribers_Base_mid_high"),
                                  which(colnames(reduced_train) == "Num_Views_Base_low"),
                                  which(colnames(reduced_train) == "Num_Views_Base_low_mid"),
                                  which(colnames(reduced_train) == "Num_Views_Base_mid_high"),
                                  which(colnames(reduced_train) == "avg_growth_low"),
                                  which(colnames(reduced_train) == "avg_growth_low_mid"),
                                  which(colnames(reduced_train) == "avg_growth_mid_high"),
                                  which(colnames(reduced_train) == "count_vids_low"),
                                  which(colnames(reduced_train) == "count_vids_low_mid"),
                                  which(colnames(reduced_train) == "count_vids_mid_high"),
                                  which(colnames(reduced_train) == "num_chars"),
                                  
                                  which(colnames(reduced_train) == "cnn_35"),
                                  which(colnames(reduced_train) == "cnn_37"),
                                  which(colnames(reduced_train) == "sd_red"),
                                  which(colnames(reduced_train) == "sd_green"),
                                  which(colnames(reduced_train) == "sd_blue"),
                                  which(colnames(reduced_train) == "cnn_0"),
                                  which(colnames(reduced_train) == "cnn_20"),
                                  which(colnames(reduced_train) == "cnn_36"),
                                  which(colnames(reduced_train) == "cnn_65"),
                                  which(colnames(reduced_train) == "num_uppercase_words"))]
# Remove all Hogs
reduced_train = reduced_train[,-c(which(colnames(reduced_train) ==
                              "hog_0"):which(colnames(reduced_train) == "hog_863"))]

# Plot of some variables of little variation
size = 5
par(mfrow = c(3, 3))
hist(train$max_blue, main = 'max_blue', cex.main = size, xlab = NULL, ylab = NULL)
hist(train$max_red, main = 'max_red', cex.main = size, xlab = NULL, ylab = NULL)
hist(train$max_green, main = 'max_blue', cex.main = size, xlab = NULL, ylab = NULL)
hist(train$min_blue, xlim = c(-10, 10), main = 'min_blue', cex.main = size, xlab = NULL, ylab = NULL)
hist(train$min_red, xlim = c(-10, 10), main = 'min_red', cex.main = size, xlab = NULL, ylab = NULL)
hist(train$min_green, xlim = c(-10, 10), main = 'min_green', cex.main = size, xlab = NULL, ylab = NULL)
hist(train$cnn_35, xlim = c(-10, 10), main = 'cnn_35', cex.main = size, xlab = NULL, ylab = NULL)
hist(train$cnn_37, xlim = c(-10, 10), main = 'cnn_37', xlab = NULL, cex.main = size, ylab = NULL)
hist(train$cnn_0, xlim = c(-10, 10), main = 'cnn_0', xlab = NULL, cex.main = size, ylab = NULL)

```

## Combine Punctuations in Training

```{r}
ex = which(colnames(reduced_train) == "punc_num_!")
fenge = which(colnames(reduced_train) == "punc_num_~")
reduced_train[,ex] = apply(reduced_train[,ex:fenge],1,sum)
reduced_train = reduced_train[,-c((ex+1):fenge)]
```

## Delete Highly Correlated Variables in Training

```{r}
cor_mat <- cor(reduced_train[,c(1:45)])
index = findCorrelation(cor_mat, 0.8)
reduced_train = reduced_train[,-index]

# Plot of correlation
melted_cor_mat = melt(cor_mat)

cor_heatmap = ggplot(data = melted_cor_mat, aes(x=Var1, y=Var2, fill=value)) + geom_tile()
cor_heatmap = cor_heatmap +
scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 0, limit = c(-1,1), space = "Lab", name="Pearson\nCorrelation") + 
theme_minimal() +
theme(axis.text.x = element_text(angle = 45, vjust = 1, size = 12, hjust = 1))

cor_heatmap


```

# Apply Models

## Backward Model Selection

```{r}
set.seed(1)
backward_selection = regsubsets(growth_2_6 ~., data = reduced_train, method = 'backward', nvmax = 47)

valid_mat = model.matrix(growth_2_6 ~., data = valid)
scores = rep(NA, 47)
for(i in 1:47){
  coefi = coef(backward_selection, id = i)
  pred = valid_mat[,names(coefi)] %*% coefi
  scores[i] = sqrt(mean((pred - valid$growth_2_6)^2))
}
barplot(height = scores, names.arg = 1:47)

rmse_back_selection = min(scores)
```

## Regularization

```{r}
reduced_valid = valid[,-c(1,2)]
reduced_valid = reduced_valid[,-c(which(colnames(reduced_valid) == "max_red"),
                                  which(colnames(reduced_valid) == "min_red"),
                                  which(colnames(reduced_valid) == "max_green"),
                                  which(colnames(reduced_valid) == "min_green"),
                                  which(colnames(reduced_valid) == "max_blue"),
                                  which(colnames(reduced_valid) == "min_blue"),
                                  which(colnames(reduced_valid) == "Num_Subscribers_Base_low"),
                                  which(colnames(reduced_valid) == "Num_Subscribers_Base_low_mid"),
                                  which(colnames(reduced_valid) == "Num_Subscribers_Base_mid_high"),
                                  which(colnames(reduced_valid) == "Num_Views_Base_low"),
                                  which(colnames(reduced_valid) == "Num_Views_Base_low_mid"),
                                  which(colnames(reduced_valid) == "Num_Views_Base_mid_high"),
                                  which(colnames(reduced_valid) == "avg_growth_low"),
                                  which(colnames(reduced_valid) == "avg_growth_low_mid"),
                                  which(colnames(reduced_valid) == "avg_growth_mid_high"),
                                  which(colnames(reduced_valid) == "count_vids_low"),
                                  which(colnames(reduced_valid) == "count_vids_low_mid"),
                                  which(colnames(reduced_valid) == "count_vids_mid_high"),
                                  which(colnames(reduced_valid) == "num_chars"),

                                  which(colnames(reduced_valid) == "cnn_35"),
                                  which(colnames(reduced_valid) == "cnn_37"),
                                  which(colnames(reduced_valid) == "sd_red"),
                                  which(colnames(reduced_valid) == "sd_green"),
                                  which(colnames(reduced_valid) == "sd_blue"),
                                  which(colnames(reduced_valid) == "cnn_0"),
                                  which(colnames(reduced_valid) == "cnn_20"),
                                  which(colnames(reduced_valid) == "cnn_36"),
                                  which(colnames(reduced_valid) == "cnn_65"),
                                  which(colnames(reduced_valid) == "num_uppercase_words"))]
# Remove all Hogs
reduced_valid = reduced_valid[,-c(which(colnames(reduced_valid) == "hog_0"):which(colnames(reduced_valid) == "hog_863"))]
reduced_valid[,ex] = apply(reduced_valid[,ex:fenge],1,sum)
reduced_valid = reduced_valid[,-c((ex+1):fenge)]
reduced_valid = reduced_valid[,-index]
train_matrix <- model.matrix(growth_2_6 ~.,reduced_train)[,-which(colnames(reduced_train) == "growth_2_6")]
valid_matrix <- model.matrix(growth_2_6 ~.,reduced_valid)[,-which(colnames(reduced_valid) == "growth_2_6")]
train_y <- reduced_train$growth_2_6

lasso <- glmnet(train_matrix, train_y,alpha = 1, standardize = TRUE)
ridge = glmnet(train_matrix, train_y,alpha = 0, standardize = TRUE)
pred_lasso <- predict(lasso, newx = valid_matrix)
pred_ridge = predict(ridge, newx = valid_matrix)
rmse_lasso = sqrt(mean((pred_lasso - valid$growth_2_6)^2))
rmse_ridge = sqrt(mean((pred_ridge - valid$growth_2_6)^2))

```

## Principal Component Analysis

```{r}
pcr_model = pcr(growth_2_6 ~., data = reduced_train, scale = T, validation = 'CV')

pred = predict(pcr_model, valid)

rmse_pcr = sqrt(mean((pred - valid$growth_2_6)^2))
```

## Partial Least Squares

```{r}
pls_model = plsr(growth_2_6 ~., data = reduced_train, scale = T, validation = 'CV')

pred = predict(pls_model, valid)

rmse_pls = sqrt(mean((pred - valid$growth_2_6)^2))
```


## Bagging

```{r}
names(reduced_train) <- make.names(names(reduced_train))
bagging <- randomForest(growth_2_6 ~., data = reduced_train,
                   mtry = 47,
                   ntree = 600, importance = TRUE)
pred_bagging = predict(bagging, valid)
rmse_bagging = sqrt(mean((pred_bagging - valid$growth_2_6)^2))
```

## Random Forest

```{r}
names(reduced_train) <- make.names(names(reduced_train))
recommended.mtry <- 16
rf <- randomForest(growth_2_6 ~., data = reduced_train,
                   mtry = recommended.mtry,
                   ntree = 600, importance = TRUE)
pred_rf = predict(rf, valid)
rmse_rf = sqrt(mean((pred_rf - valid$growth_2_6)^2))

# Plot importance of predictors
imp = varImpPlot(rf)
col_fun = colorRampPalette(c('red', 'blue'))
cols = col_fun(10)
barplot(sort(imp[,1], decreasing = T)[1:10], ylab = '%IncMSE', col = cols, main = NULL, names.arg = NULL)
```


## Boosting

```{r}
boost = gbm(growth_2_6~.,distribution = "gaussian",
            data = reduced_train,n.trees = 700,
            interaction.depth = 9,shrinkage = 0.03,
            cv.folds = 6, n.cores = NULL,
            verbose = F)
pred_boost = predict(boost, valid)
rmse_boost = sqrt(mean((pred_boost - valid$growth_2_6)^2))
```

## Comparing All Models

```{r}
rmses = c('back selection' = rmse_back_selection, 'bagging' = rmse_bagging, 'boost' = rmse_boost, 'lasso' = rmse_lasso, 'pcr' = rmse_pcr, 'pls' = rmse_pls, 'rf' = rmse_rf, 'ridge' = rmse_ridge)

cols = col_fun(8)
barplot(sort(rmses), names.arg = names(sort(rmses)), horiz = T, col = cols)
```

# Tuning

```{r}
# mtry
mtry1 = c(15, 17, 19, 21, 23, 25, 27, 30, 33, 35)
rsebest<-rep(0, len(mtry1))
for(i in 1:len(mtry1)){
  rf <- randomForest(growth_2_6 ~., data = train12, mtry = mtry1[i], ntree = 600, importance = TRUE)
  pred_rf = predict(rf, valid)
  rmse_rf = sqrt(mean((pred_rf - valid$growth_2_6)^2))
  rsebest[i] <- rmse_rf
}
plot(mtry1, rsebest, xlab = "mtry range",ylab = "RMSE",main = "mtry change in RMSE",cex.main = 1.6)

# ntree for mtry=27
ntree1 = c(500,550,600,650,700,750,800)
rsebest1 <- rep(0,len(mtry1))
for(i in 1:len(ntree1)){
  rf <- randomForest(growth_2_6 ~., data = train12, mtry = 27, ntree = ntree[i],importance = TRUE)
  pred_rf = predict(rf, valid)
  rmse_rf = sqrt(mean((pred_rf - valid$growth_2_6)^2))
  rsebest1[i]<-rmse_rf
}
plot(ntree1, rsebest1, xlab = "mtry range",ylab = "RMSE",main="ntree change in RMSE",cex.main=1.6)

# ntree for mtry=33
ntree1=c(500,550,600,650,700,750,800)
rsebest1<-rep(0,len(mtry1))
for(i in 1:len(ntree1))
{
  rf <- randomForest(growth_2_6 ~., data = train12, mtry = 33, ntree = ntree[i], importance = TRUE)
  pred_rf = predict(rf, valid)
  rmse_rf = sqrt(mean((pred_rf - valid$growth_2_6)^2))
  rsebest1[i]<-rmse_rf
}
plot(ntree1, rsebest1, xlab = "mtry range",ylab = "RMSE",main = "ntree change in RMSE",cex.main = 1.6)

# ntree for mtry=35
ntree1=c(500,550,600,650,700,750,800)
rsebest1 <- rep(0, len(mtry1))
for(i in 1:len(ntree1)){
  rf <- randomForest(growth_2_6 ~., data = train12, mtry = 35, ntree = ntree[i], importance = TRUE)
  pred_rf = predict(rf, valid)
  rmse_rf = sqrt(mean((pred_rf - valid$growth_2_6)^2))
  rsebest1[i]<-rmse_rf
}
plot(ntree,rsebest1, xlab = "mtry range",ylab = "RMSE",main="ntree change in RMSE",cex.main=1.6)

# combination
mtry4=matrix(c(27,600,30,600,33,800),ncol=2,byrow = T)
rsebest1<-rep(0,3)
for(i in 1:len(ntree1)){
  rf <- randomForest(growth_2_6 ~., data = train12, mtry = mtry4[i,1], ntree = mtry4[i,2], importance = TRUE)
  pred_rf = predict(rf, valid)
  rmse_rf = sqrt(mean((pred_rf - valid$growth_2_6)^2))
  rsebest1[i]<-rmse_rf
}
plot(c(1:3),rsebest)
```

# Fit the Model to Whole Training & Predict Testing Data

```{r, eval=FALSE}
set.seed(1)
trainIndex <- createDataPartition(training$growth_2_6, p = 0.99, list = FALSE)
train <- training[trainIndex, ]
valid <- training[-trainIndex, ]

reduced_train = train[,-c(1, 2)]
reduced_train = reduced_train[,-c(which(colnames(reduced_train) == "max_red"),
                                  which(colnames(reduced_train) == "min_red"),
                                  which(colnames(reduced_train) == "max_green"),
                                  which(colnames(reduced_train) == "min_green"),
                                  which(colnames(reduced_train) == "max_blue"),
                                  which(colnames(reduced_train) == "min_blue"),
                                  which(colnames(reduced_train) == "Num_Subscribers_Base_low"),
                                  which(colnames(reduced_train) == "Num_Subscribers_Base_low_mid"),
                                  which(colnames(reduced_train) == "Num_Subscribers_Base_mid_high"),
                                  which(colnames(reduced_train) == "Num_Views_Base_low"),
                                  which(colnames(reduced_train) == "Num_Views_Base_low_mid"),
                                  which(colnames(reduced_train) == "Num_Views_Base_mid_high"),
                                  which(colnames(reduced_train) == "avg_growth_low"),
                                  which(colnames(reduced_train) == "avg_growth_low_mid"),
                                  which(colnames(reduced_train) == "avg_growth_mid_high"),
                                  which(colnames(reduced_train) == "count_vids_low"),
                                  which(colnames(reduced_train) == "count_vids_low_mid"),
                                  which(colnames(reduced_train) == "count_vids_mid_high"),
                                  which(colnames(reduced_train) == "num_chars"),
                                  
                                  which(colnames(reduced_train) == "cnn_35"),
                                  which(colnames(reduced_train) == "cnn_37"),
                                  which(colnames(reduced_train) == "sd_red"),
                                  which(colnames(reduced_train) == "sd_green"),
                                  which(colnames(reduced_train) == "sd_blue"),
                                  which(colnames(reduced_train) == "cnn_0"),
                                  which(colnames(reduced_train) == "cnn_20"),
                                  which(colnames(reduced_train) == "cnn_36"),
                                  which(colnames(reduced_train) == "cnn_65"),
                                  which(colnames(reduced_train) == "num_uppercase_words"))]
# Remove all Hogs
reduced_train = reduced_train[,-c(which(colnames(reduced_train) ==
                              "hog_0"):which(colnames(reduced_train) == "hog_863"))]
reduced_train = reduced_train[,-index]

ex = which(colnames(reduced_train) == "punc_num_!")
fenge = which(colnames(reduced_train) == "punc_num_~")
reduced_train[,ex] = apply(reduced_train[,ex:fenge],1,sum)
reduced_train = reduced_train[,-c((ex+1):fenge)]

names(reduced_train) <- make.names(names(reduced_train))
recommended.mtry <- 16
rf <- randomForest(growth_2_6 ~., data = reduced_train,
                   mtry = recommended.mtry,
                   ntree = 600, importance = TRUE)
pred_rf_test = predict(rf, testing)

bagging <- randomForest(growth_2_6 ~., data = reduced_train,
                   mtry = 47,
                   ntree = 600, importance = TRUE)

pred_bagging_test = predict(bagging, testing)
```

# Generate CSV file

```{r,eval=FALSE}
result= data.frame("id" = c(7242:10346), "growth_2_6"= pred_bagging_test, row.names = NULL)
result_csv = write.csv(result, file = "result.csv",row.names = FALSE)
```

# Exploratory Analysis (Graphics)
```{r}
ggplot(data = reduced_train,aes(x=avg_growth,y=growth_2_6))+
  geom_boxplot(fill = c("pink","grey","grey","grey"))+
  xlab("Average growth between 2-6 hours on this channel") +
  ylab("Growth Rate between 2-6 hours")+
  scale_x_discrete(labels= c("High","Low","Low-Mid","Mid-High"))
ggplot(data = reduced_train,aes(x=Num_Views_Base,y=growth_2_6))+
  geom_boxplot(fill = c("pink","grey","grey","grey"))+
  xlab("Number of view base in the channel") +
  ylab("Growth Rate between 2-6 hours")+
  scale_x_discrete(labels= c("High","Low","Low-Mid","Mid-High"))
ggplot(data = reduced_train,aes(x=dow,y=growth_2_6))+
  geom_boxplot(fill = c("pink","grey","grey","grey","pink","pink","grey"))+
  xlab("Date of the week") +
  ylab("Growth Rate between 2-6 hours")+
  scale_x_discrete(labels= c("Monday","Tuesday","Wednesday","Thursday","Friday","Saturday","Sunday"))
ggplot(data = reduced_train,aes(x=Duration,y=growth_2_6))+
  geom_point(color = "black")+
  geom_vline(xintercept = 800, color = "red", size=1.5)+
  xlim(0,10000)+
  xlab("Duration of the video") +
  ylab("Growth Rate between 2-6 hours")
ggplot(data = reduced_train,aes(x=num_uppercase_chars,y=growth_2_6))+
  geom_point(color = "darkgrey")+
  xlim(0,40)+
  geom_vline(xintercept = c(0.8,17), color = "red", size=1)+
  xlab("Number of uppercase characters") +
  ylab("Growth Rate between 2-6 hours")
```